Trends of SDR in Thessaloniki

### 2023-07-20 Article.Rmd
Commit 2023-07-20 20:14

For completeness, we will provide below a brief overview of the [....Csid
term is referenced above....]{.comment-start id="0" author="A N"
date="2023-07-15T20:00:52Z"}CSid algorithm[]{.comment-end id="0"}, along
with the site specific thresholds.
To calculate the reference clear sky
$\text{SDR}_\text{CSref}$ we used the [....Not visible equation....]{.comment-start id="2"
author="A N" date="2023-07-15T19:23:34Z"}${}_{}$[[]{.comment-end
id="2"}]{.insertion author="A N" date="2023-07-15T19:23:34Z"} derive by
the radiation model of @Haurwitz1945, adjusted for our site with a
factor $a$, resulted by an iterative optimization process, as described
by @Long2000 and @Reno2016.
The target of
the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and
was accomplished with the computing function [\...notation
"library::function"....]{.comment-start id="2" author="A N"
date="2023-07-15T20:08:20Z"}"stats::optimise"[]{.comment-end id="2"}
of the R language [@RCT2023], with an implementation based on the work of @Brent1973. 
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), [....rephrased....]{.comment-start id="3" author="A N" date="2023-07-15T20:32:50Z"}while the whole procedure, manages to characterize large amount of our data[]{.comment-end id="3"}. Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.

@@

where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is the tested model clear sky radiation.

@@

where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{w}\;\text{m}^{-2}$.

@@

The mean of the measured value $\overline{\text{SDR}}_i = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$ must be inside an envelope based on the equivalent mean of the reference model $\overline{\text{SDR}}_\text{CSref} = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq. \ref{eq:MeanVIP}).

@@

The running max measured value $M_{\text{SDR},i} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$, is compared to a similar constructed value from the reference $M_{CSi} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq.\ \ref{eq:MaxVIP}).

\begin{equation}
`r MaxVIP_fct` \times M_{CSi} - `r MaxVIP_off_low`
< M_{\text{SDR},i} <
`r MaxVIP_fct` \times M_{CSi} + `r MaxVIP_off_upp`
\label{eq:MaxVIP}
\end{equation}

>>>>

For completeness, we will provide below a brief overview of the [....Csid
term is referenced above....]{.comment-start id="0" author="A N"
date="2023-07-15T20:00:52Z"}CSid algorithm[]{.comment-end id="0"}, along
with the site specific thresholds.
To calculate the reference clear sky
$\text{SDR}_\text{CSref}$ we used the [....Not visible equation....]{.comment-start id="2"
author="A N" date="2023-07-15T19:23:34Z"}${}_{}$[[]{.comment-end
id="2"}]{.insertion author="A N" date="2023-07-15T19:23:34Z"} derive by
the radiation model of @Haurwitz1945, adjusted for our site with a
factor $a$, resulted by an iterative optimization process, as described
by @Long2000 and @Reno2016.
The target of
the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and
was accomplished with the computing function [\...notation
"library::function"....]{.comment-start id="2" author="A N"
date="2023-07-15T20:08:20Z"}"stats::optimise"[]{.comment-end id="2"}
of the R language [@RCT2023], with an implementation based on the work of @Brent1973. 
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), [....rephrased....]{.comment-start id="3" author="A N" date="2023-07-15T20:32:50Z"}while the procedure, manages to characterize the majority of our data[]{.comment-end id="3"}. Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.

@@

where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is the tested model of clear sky radiation.

@@

where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{w}\,\text{m}^{-2}$.

@@

a) Mean of the measured $\overline{\text{SDR}}_i$ <!--= \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$--> and running mean of the reference $\overline{\text{SDR}}_{\text{CSref},i}$ <!-- = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$--> (Eq. \ref{eq:MeanVIP}).

@@

<!-- The running max measured value $M_{\text{SDR},i} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$, is compared to a similar constructed value from the reference $M_{CSrefi} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq.\ \ref{eq:MaxVIP}). -->

b) Maximum measured value $M_{\text{}}$, and maximum reference $M_{\text{CSref}}$ (Eq.\ \ref{eq:MaxVIP}).

\begin{equation}
`r MaxVIP_fct` \times M_{\text{CSref},i} - `r MaxVIP_off_low`
< M_{\text{}i} <
`r MaxVIP_fct` \times {\text{CSref},i} + `r MaxVIP_off_upp`
\label{eq:MaxVIP}
\end{equation}
